Damage localization based on vibrations

### 2016-12-04 slides/slides.tex
Skide update intro
physical models
Ajout slides : state of the art : :+1:

@@

\section{Introduction}

\begin{frame}{Bridge}
\begin{center}
\includegraphics[width=4cm]{images/crack.jpg}

\pause

\includegraphics[width=5cm]{images/bridge.png}
\end{center}
\end{frame}

\begin{frame}{Damage and SHM}
\begin{exampleblock}{Damages}
Changes in a system that negatively affect its performance.
\end{exampleblock}

\begin{exampleblock}{Structure Health Monitoring}
A damage identification strategy for aerospace, civil and mechanical structures.
\end{exampleblock}

@@

\begin{frame}{Why we do that}
\end{frame}

\begin{frame}{4 levels}
\begin{center}
\begin{itemize}
\item Detection: Is the structure damaged or not?
\item Localization: Where is the damaged area located?
\item Quantification: What is the extent of damage?
\item Prediction: What is the remaining service life of the structure?
\end{itemize}
\end{center}
\end{frame}

\begin{frame}{transition/plan}
\end{frame}

@@

\begin{frame}{intro}
\end{frame}

\begin{frame}{Model based methods}
\end{frame}

\begin{frame}{Data driven methods}
\end{frame}

\begin{frame}{Combined methods}
\end{frame}

@@

\begin{frame}{Finite Elements model}

@@

\begin{frame}{Continous-time state-space model}
With the variable change $x =
\begin{pmatrix}
\dot{q} \\
q
\end{pmatrix}$, we have:

@@

\begin{frame}{Discret-time state-space model}

@@

\begin{frame}{FRF Interpolation Method}

@@

\begin{frame}{Interpolation}
Cubic polynomial spline interpolation:

@@

@@

\begin{frame}{Error calcul}

For each sensor:
\begin{center}
$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
\end{center}

Difference with the reference state:
\begin{center}
$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
\end{center}

\begin{frame}{Probability of identification of a damage}
\begin{center}
\includegraphics[height=4cm]{images/gaussiennes.png}
\end{center}
\end{frame}

@@

\begin{frame}{System masses-springs}
\begin{center}
\includegraphics[width=5cm]{images/ressorts.png}

@@

@@

\begin{frame}{Sample frequency and Discret-time state-space model}

@@

\begin{frame}{FRF and Interpolation}
\end{frame}

\begin{frame}{Results}
\begin{center}
\includegraphics[width=5cm]{images/FRF_freq.png}

@@

\begin{frame}{Results}
\begin{center}
\includegraphics[width=5cm]{images/curve_damage.png}

@@

\begin{frame}{Results}
\end{frame}

>>>>

  \setbeamertemplate{navigation symbols}{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Purpose}
\begin{frame}{Purpose}

\begin{columns}
		\begin{column}{0.5\textwidth} 
		\begin{center}
			\includegraphics[width=5cm]{images/crack.jpg}
		\end{center}
		\end{column}
		\begin{column}{0.7\textwidth}
		\begin{center}
			\pause
			\includegraphics[width=6cm]{images/minneapolis.jpg}
		\end{center}
		\end{column}
	\end{columns}

\vspace{1\baselineskip}
\begin{itemize}
\item ``Better safe than sorry."
\vspace{1\baselineskip}
\item Example: accelerate inspection of post-earthquake damage.
\end{itemize}
\end{frame}

\subsection{Definitions}

\begin{frame}{Definitions}
\begin{exampleblock}{Damages}
Changes in a system that negatively affect its performance.
\end{exampleblock}
\begin{center}
	\includegraphics[width=4.5cm]{images/crack.jpg}
\end{center}
\begin{exampleblock}{Structure Health Monitoring}
A damage identification strategy for aerospace, civil and mechanical structures.
\end{exampleblock}

@@

\subsection{4 levels in damage identification}
\begin{frame}{4 levels in damage identification}

\begin{center}
\begin{itemize}[<+->]
\item Detection: Is the structure damaged or not?
\vspace{1\baselineskip}
\item Localization: Where is the damaged area located?
\vspace{1\baselineskip}
\item Quantification: What is the extent of damage?
\vspace{1\baselineskip}
\item Prediction: What is the remaining service life of the structure?
\end{itemize}
\end{center}
\end{frame}

\subsection{Tools}
\begin{frame}{Tools}
\begin{block}{Traditional methods}
Visual inspections or experimental techniques (such as radiography or ultrasound)
\end{block}

\setbeamertemplate{itemize item}{\color{green}$\checkmark$}
\begin{columns}
		\begin{column}{0.5\textwidth} 
		\begin{center}
			\begin{itemize}
				\item Detailed information about a local damage state
			\end{itemize}
		\end{center}
		\end{column}
		\begin{column}{0.5\textwidth}
		\begin{center}
		\setbeamertemplate{itemize item}{\color{red}$\times$}
			\begin{itemize}
				\item Requires to know area where it is located
				\item May be costly
				\item Taking a long time to be performed
				\item Hope for easy access
			\end{itemize}
		\end{center}
		\end{column}
	\end{columns}
	\pause
	\begin{center}
	\textcolor{red}{{\large 
$\Rightarrow$ Global methods automated and based on sensor measurements were developed.}}

@@

\subsection{Vibration-based damage identification}
\begin{frame}{Vibration-based damage identification}
\begin{block}{General idea}
	Damage affects the physical properties (mass, damping, and stiffness) of the structure.\newline

	$\Rightarrow$ This will cause detectable changes in modal properties (natural frequencies, modal damping, and mode shapes).
\end{block}
\begin{itemize}
\item Example: Cracks cause reductions in stiffness.
\end{itemize}
\vspace{0.5\baselineskip}
\begin{center}
\textcolor{red}{{\large Two differents methods : model-based or data-driven.}}
\end{center}
\end{frame}

\subsection{Model based methods}
\begin{frame}{Model based methods}
\begin{center}
\begin{itemize}
\item Damage is identified through the updating of a finite element (FE) model.

\vspace{1\baselineskip}
\item Modal characteristics is the experimental data used for damage
assessment through FE model updating.
\vspace{1\baselineskip}
\item Different types of modal data can be used (natural frequencies, eigenvalues, etc).
\end{itemize}
\end{center}
\end{frame}

\subsection{Data driven methods}
\begin{frame}{Data driven methods}
\begin{center}
\begin{itemize}
\item Methods that use models based on experimental response data recorded on the structure.

\vspace{1\baselineskip}
\item Damage parameter $D$ is the variation of the damage feature $d$ between
the inspection $I$ and the reference $R$ configurations:

\begin{equation}
D=d_{I} - d_{R}
\end{equation}
\item Data-driven methods may be applied with a limited number of available signals (both
responses and excitations).
\end{itemize}
\end{center}

@@

\subsection{Finite Elements model}
\begin{frame}{Finite Elements model}

@@

\subsection{Continous-time state-space model}
\begin{frame}{Continous-time state-space model}
With the variable change $x =
\begin{pmatrix}
\dot{q} \\
q
\end{pmatrix}$, we have:

@@

\subsection{Discret-time state-space model}
\begin{frame}{Discret-time state-space model}

@@

\subsection{FRF Interpolation Method}
\begin{frame}{FRF Interpolation Method}

@@

\subsection{FRF calcul}
\begin{frame}{FRF calcul}
\end{frame}

\subsection{Interpolation}
\begin{frame}{Interpolation}
Cubic polynomial spline interpolation:

\subsection{Error calcul}
\begin{frame}{Error calcul}

@@

For each sensor:
$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$

Difference with the reference state:
$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$

@@

\subsection{Probability of identification of a damage}
\begin{frame}{Probability of identification of a damage}
\begin{center}
\includegraphics[height=4cm]{images/gaussiennes.png}
\end{center}
\end{frame}

@@

\subsection{System masses-springs}
\begin{frame}{System masses-springs}
\begin{center}
\includegraphics[width=5cm]{images/ressorts.png}

@@

\begin{exampleblock}{Masses}
\begin{center}
$
M = 
\begin{pmatrix} 
m_1\\ 
&\ddots\\ 
&&m_n
\end{pmatrix}
$
\end{center}
\end{exampleblock}

@@

\subsection{Sample frequency and Discret-time state-space model}
\begin{frame}{Sample frequency and Discret-time state-space model}

@@

\subsection{FRF and Interpolation}
\begin{frame}{FRF and Interpolation}
\end{frame}

\subsection{Results}
\begin{frame}{Results 1/3}
\begin{center}
\includegraphics[width=5cm]{images/FRF_freq.png}

@@

\begin{frame}{Results 2/3}
\begin{center}
\includegraphics[width=5cm]{images/curve_damage.png}

@@

\begin{frame}{Results 3/3}
\end{frame}
